Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-02 paper/paper.tex
whats that feature figure

The denoised expectation values of the parallax projected into the \cmd\ show interest features.
\begin{itemize}
\item (1) Narrow Lower Main Sequence
\item (2) Wide Upper Main Sequence
\item (3) Plausible Binary Sequence
\item (4) Prominent Red clump
\item (5) Narrow Red Giant Branch
\item (6) Noticeable turn off
\end{itemize}
The lower main sequence is very narrow while the upper main sequence is much wider. This may be an age variation on the main sequence mixed with a malquist bias of seeing a much larger volume of upper main sequence stars. There is a plausible binary sequence of stars with about twice the brightness as the main sequence. The helium burning red clump is (surprisingly) prominent for the volume DR1 probed, and the red giant branch is fairly straight and narrow. The main sequence turn off is noticeable and also surprisingly narrow, possibly a reflection of the star formation history of the local volume also mixed with a malmquist bias.

>>>>

The denoised expectation values of the parallax projected into the \cmd\ show interest features.
We visualize this \cmd\ again in Figure \ref{fig:wtf} pointing out some interesting features.
\begin{itemize}
\item (1) Narrow Lower Main Sequence
\item (2) Wide Upper Main Sequence
\item (3) Plausible Binary Sequence
\item (4) Prominent Red clump
\item (5) Narrow Red Giant Branch
\item (6) Noticeable turn off
\end{itemize}
The lower main sequence is very narrow while the upper main sequence is much wider. This may be an age variation on the main sequence mixed with a malmquist bias of seeing a much larger volume of upper main sequence stars. There is a plausible binary sequence of stars with about twice the brightness as the main sequence. The helium burning red clump is (surprisingly) prominent for the volume DR1 probed, and the red giant branch is fairly straight and narrow. The main sequence turn off is noticeable and also surprisingly narrow, possibly a reflection of the star formation history of the local volume also mixed with a malmquist bias.
